\documentclass[]{letter}
\usepackage{hyperref}
\usepackage[abbr]{harvard}
\addtolength{\textwidth}{1.3in}
\addtolength{\oddsidemargin}{-0.65in}
\addtolength{\textheight}{1.0in}
\addtolength{\topmargin}{-0.6in}
\renewcommand{\baselinestretch}{1.48}
\newtheorem{coro}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{exam}{Example}
\newtheorem{theo}{Theorem}
\newtheorem{defi}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}
\newtheorem{prop}{Proposition}
\usepackage{times}
%\usepackage[active]{srcltx}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{caption}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{booktabs}
%\usepackage{epstopdf}
\begin{document}

\begin{letter}{Sr. Director \\ Economics Technology R\&D \\ SAS Institute Inc
		\\ SAS Campus Drive \\ Cary, NC. 27513}
	\opening{Hello, Mark:}

I am a doctoral candidate in the department of Economics in NC state University. I received a email from our director that  your department is looking for a graduate student specialized on time series econometrics. I believe I am a qualified candidate for this position for the experience I have.

\paragraph{Experience  with econometrics}
I have finished 10 classes related to statistics and econometrics during my last 3 years of graduate studying (class details see attached transcript). I have been a teaching assistant for Phd level econometrics courses in our department for one year which include ECG751 Econometrics method and ECG752 time series econometrics. I am currently working a paper in financial econometrics modeling price volatility with my advisor Dr Pelletier. My dissertation will also be  based on such field. 

Experience with programming
My first experience in SAS was processing and modeling with big data for my course paper in year 2013. Then I attended 2014 summer session of SAS taught by a nice lady Joy Smith in department of statistics. To keep doing some work in SAS, I enrolled in ST555 statistical programming in 2015 Spring semester which taught SAS in 80\% time and R in 20\%. The next step in my plan is to learn some macro programming in SAS. I am enthusiastic in programming. Since I need to do my research with matlab by the request of my advisor, I took a course in computer science in 2014 fall. The formal training of programming give me a sense of how to writing code in good habits. In short, I like programing and plan to start my career in this field.

Experience with technical writing
I use \LaTex\ to write my thesis and this cover letter. I used R markdown in ST 555 for homework assignment.



list of supplemental materials:
Some code in my research        https://github.com/crazylaoshen



\signature{Ji Shen}
\closing{Best Regards,}

\ps
P.S. You can find Some code in my research at
\url{https://github.com/crazylaoshen}.

\end{letter}
\end{document}